Exploration of the MIRT solutions

### 2024-09-03 notebooks/Mirt_solution_exploration.Rmd

---
title: 'Exploration of the MIRT solutions'
output:
  html_document: 
    df_print:        paged
    code_folding:    show
    toc:             yes
    toc_float:       yes
editor_options: 
  chunk_output_type: inline
---

```{r setup}
#| message: false
library(knitr)
library(mirt)
library(tidyverse)

@@

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = TRUE,
  message  = FALSE,
  cache    = FALSE,
  results  = 'hold'
)

>>>>

---
title: 'Exploration of the MIRT solutions'
output:
  word_document:
    df_print:        kable
    toc:             yes
    reference_docx:  ../www/Notebook_template.docx
  html_document:
    df_print:        paged
    code_folding:    show
    toc:             yes
    toc_float:       yes
editor_options: 
  chunk_output_type: inline
---

```{r setup}
#| echo: !expr 'knitr::is_html_output()'
#| message: false
library(knitr)
library(mirt)
library(tidyverse)

@@

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = is_html_output(),
  message  = FALSE,
  cache    = FALSE,
  results  = 'hold'
)
